Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
removed appendix about observable systems
wording

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. It does this by assuming some 
precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.

>>>>

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. For this purpose, it assumes some
precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The
checks that these assumptions are sound are performed by subsequent
{\sc verify} stages.
